25 Years of Water Quality Change in Rhode Island Lakes and Ponds

### 2018-11-02 manuscript/manuscript.Rmd
Refined URIWW acronym

The study area for this analyis includes data in lakes and ponds in the state of Rhode Island that were collected by the University of Rhode Island's Watershed Watch (RIWW) program (Figure X).  MORE DETAILS ON RIWW.

>>>>

The study area for this analyis includes data in lakes and ponds in the state of Rhode Island that were collected by the University of Rhode Island's Watershed Watch (URIWW) program (Figure X).  MORE DETAILS ON RIWW.
